Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-07-21 docs/paper/paper.Rmd
update paper

```{r relative-interval-score}
relative_interval_score <- scores |>
  calc_relative_score(
    cols = c("location", "target_end_date", "horizon", "range")
  )
wis <- scores |>
  summarise_scores(
    by = c("location_name", "target_end_date", "horizon", "model")
  )
relativ_wis <- wis |>
  calc_relative_score(cols = c("location_name", "target_end_date", "horizon"))
```

>>>>

```{r relative-interval-score}
relative_interval_score <- scores |>
  calc_relative_score(
    cols = c("location", "target_end_date", "horizon", "range")
  )
wis <- scores |>
  summarise_scores(
    by = c("location_name", "target_end_date", "horizon", "model")
  )
relative_wis <- wis |>
  calc_relative_score(cols = c("location_name", "target_end_date", "horizon"))
```
